\chapter{Technical Specification}

The Vanna-Volga pricing method is a technique used to price first generation exotic options in foreign exchange market. This method derives from the trader's idea that the difference between market price and Black-Scholes price is the volatility smile impact, which could be adjusted with costs incurred by hedging three main risks associated to the volatility of the option: the Vega, the Vanna and the Volga.

\section{Greeks} 
The foreign exchange spot process is considered to follow Geometric Brownian motion (GBM). Thus we find the results we are able to obtain in equity markets hold in the case of FX options as well. \newline
Then the Black-Scholes value of call option is:
\begin{align}
V_{call} &= Se^{-r_fT}N(d_1) - Ke^{-r_dT}N(d_2) \\
V_{put} &=  Ke^{-r_dT}N(-d_2) - Se^{-r_fT}N(-d_1)
\end{align}
where 
\[d_1 = \frac{ln\frac{S}{K}+\left( r_d - r_f +\frac{\sigma^2}{2}T\right) }{\sigma\sqrt{T}}\]
\[d_2 = d_1 - \sigma \sqrt{T}\]
and $r_d$ and $r_f$ are the domestic and foreign risk free rate, respectively. $T$ is the time to maturity. $N$ denotes as the cumulative density function of standard normal distribution. Below we will discuss the Greeks in the context of Black-Scholes model.

\subsection{Vega}
Vega $\nu$ is the first derivative of the option value with respect to the volatility $\sigma$. 
\newline
\newline
By taking the derivative we have
\begin{align}
&\begin{aligned}
\nu_C &=\frac{\partial C}{\partial \sigma} = Se^{-r_fT}\varPhi(d_1)\frac{\partial d_1}{\partial \sigma}-Ke^{-r_dT}\varPhi(d_2)\frac{\partial d_2}{\partial \sigma}\\
&= Se^{-r_fT}\varPhi(d_1)\frac{d_1 - d_2}{\sigma} \\
&=  Se^{-r_fT}\varPhi(d_1)\sqrt{T}
\end{aligned} \\
&\begin{aligned}
\nu_P &=\frac{\partial P}{\partial \sigma} =-Ke^{-r_dT}\varPhi(d_2)\frac{\partial d_2}{\partial \sigma} + Se^{-r_fT}\varPhi(d_1)\frac{\partial d_1}{\partial \sigma}\\
&= \nu_C 
\end{aligned}
\end{align}

\subsection{Vanna}
Vanna is the second order derivative of the option value, once to the volatility $\sigma$ and once to the initial spot price. 
\newline
\newline
By taking the derivative we have:
\begin{align}
&\begin{aligned}
Vanna_C &= \frac{\partial^2 C}{\partial S \partial \sigma} = \frac{\partial \Delta_C}{\partial \sigma} = e^{-r_fT}\varPhi(d_1)\frac{\partial d_1}{\partial \sigma} \\
&= e^{-r_fT}\varPhi(d_1)\left( \sqrt{T} - \frac{d_1}{\sigma}\right) \\
&= -\frac{d_2}{S\sigma \sqrt{T}}\nu_C
\end{aligned} \\
&\begin{aligned}
Vanna_P &= \frac{\partial^2 P}{\partial S \partial \sigma} = \frac{\partial \Delta_P}{\partial \sigma} = e^{-r_fT}\varPhi(d_1)\frac{\partial d_1}{\partial \sigma} \\
&= Vanna_C
\end{aligned}
\end{align}

\subsection{Volga}
Volga is the second order derivative of the option value with respect to the volatility $\sigma$ twice. 
\newline
\newline
By taking the derivative we have:
\begin{align}
&\begin{aligned}
Volga_C &= \frac{\partial^2 C}{\partial^2 \sigma} = \frac{\partial \nu_C}{\partial \sigma} = e^{-r_fT}S\sqrt{T}\frac{\partial \varPhi(d_1)}{\partial d_1}\frac{\partial d_1}{\partial \sigma} \\
&= e^{-r_fT}S\sqrt{T}\varPhi(d_1)\frac{d_1d_2}{\sigma} \\
&= \frac{\nu_C d_1d_2}{\sigma}
\end{aligned} \\
&\begin{aligned}
Volga_P &= \frac{\partial^2 P}{\partial^2 \sigma} = \frac{\partial \nu_P}{\partial \sigma} = \frac{\partial \nu_C}{\partial \sigma}  \\
&= Volga_C
\end{aligned}
\end{align}

\section{Model Framework and Equations}
\subsection{Model Inputs}
As shown above, the key inputs are:
\begin{itemize}
	\item The foreign exchange rate. Published real-time in Bloomberg terminal.
	\item The interest rate from each country.
	\item The volatility matrix in the bid/ask format in terms of ATM, 25$\Delta$ and 10$\Delta$ butterflies and risk reversals.
	\item The maturity time.
\end{itemize}

\subsection{The Simplified Vanna-Volga Process}
The simplified formulation of the Vanna-Volga pricing method could be found in several publications: Wystup (2006), Castagna and Mercurio (2006) and Bossens et al. (2010).
The equation is given by:
\begin{align}
X^{VV} &= X^{BS} + \frac{Vanna(X)}{Vanna(RR)}RR_{cost}+ \frac{Volga(X)}{Volga(BF)}BF_{cost}
\end{align}
where
\begin{align}
&\begin{aligned}
RR_{cost} &= \left[Call\left( K_C,\sigma\left( K_C\right) \right) -Put\left( K_p,\sigma\left( K_p\right) \right)\right] \\
&\quad - \left[Call\left( K_C,\sigma_0 \right) -Put\left( K_p,\sigma_0 \right)\right]
\end{aligned} \\
&\begin{aligned}
BF_{cost} &= \frac{1}{2} \left[Call\left( K_C,\sigma\left( K_C\right) \right) +Put\left( K_p,\sigma\left( K_p\right) \right)\right] \\
&\quad - \frac{1}{2}\left[Call\left( K_C,\sigma_0 \right) + Put\left( K_p,\sigma_0 \right)\right]
\end{aligned}
\end{align}
and $X^{BS}$ denotes the Black-Scholes price of the vanilla option, Vanna and Volga of option $X$ are calculated with ATM volatility. \newline
\newline
It is worth noting that in this version of the Vanna-Volga pricing model, a small but non-zero fraction of Volga carried by RR and a small fraction of Vanna carried by BF are not taken into account. The risk associated with Vega is also neglected here.

\subsection{Model Outputs}
The outputs would be:
\begin{itemize}
	\item 25$\Delta$ and 10$\Delta$ butterflies cost
	\item 25$\Delta$ and 10$\Delta$ risk reversals cost
	\item Greeks. Vanna for option and risk reversals strategy, Volga for option and butterflies strategy.
	\item Vanna-Volga method corrected option price.
\end{itemize}