\cleardoublepage
%\pagebreak
\phantomsection
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}

\bibitem{citation-1}Black, F., and Scholes, M. (1973). 'The pricing of Options and Corporate Liabilities',\ \textit{Journal of Political Economy}

\bibitem{citation-2} Bossens, F., Rayee, G., Skantzos, N.S. and Deelstra, G. (2010). 'Vanna-volga methods applied to FX derivatives. From theory to market practice',\ \textit{Working Paper}

\bibitem{citation-3} Castagna, A. and Mercurio, F. (2006). 'Consistent pricing of FX options',\ \textit{Working Papers Series}

\bibitem{citation-4} Castagna, A. and Mercurio, F. (2007). 'The vanna-volga method for implied volatilities',\ \textit{Risk}

\bibitem{citation-5} Carr, P., Hogan, A. and Verma, A. (2006). 'Vanna-volga method for 1st generation exotics
in FX',\ \textit{Bloomberg Research Paper}

\bibitem{citation-6} Fisher, T. (2007). 'Variations on the vanna-volga adjustment',\ \textit{Bloomberg Research Paper}

\bibitem{citation-7} Shkolnikov, Y. (2009). 'Generalized vanna-volga method and its applications',\ \textit{NumeriX Research Paper}

\bibitem{citation-8} Wystup, U. (2006).\ \textit{FX Options and Structured Products} Wiley Finance

\bibitem{citation-9} Wystup, U. (2008). 'Pricing of First Generation Exotics with the Vanna-Volga Method: Pros and Cons',\ \textit{Centre for Practical Quantitative Finance Working Paper Series}

\bibitem{citation-10} Janek, A. (2011). 'The vanna-volga method for derivative pricing',\ \textit{MPRA Paper} 

\bibitem{citation-11} Xiong, C. (2011). 'Vanna-Volga Method for Foreign Exchange Implied Volatility Smile',\ \textit{University of Utah Working Paper} 



\end{thebibliography}
